---
title: "assignment_7"
author: "Wouter"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(dslabs)
library(readr)
library(DBI)
```

# assignment_7

1. Load the flu (“./data/flu_data.csv), the dengue (.”/data/dengue_data.csv) and the gapminder ({dslabs} package) into three separate dataframes in R

```{r}
# lees de data in
fluDf <- read_csv(here("assignment_7", "flu_data.csv"), skip = 11)
dengueDf <- read_csv(here("assignment_7", "dengue.csv"), skip = 11)
gapminderDf <- data.frame(gapminder)

# maak de griep en dengue data tidy want er zaten meerdere observaties op 1 rij
tidyFlu <- fluDf %>% pivot_longer(cols=tail(colnames(fluDf), n= 29), names_to= "country", values_to= "activity")
tidyDengue <- dengueDf %>% pivot_longer(cols= tail(colnames(dengueDf), n= 10), names_to= "country", values_to= "activity")

# maak de datatype voor de country en year kolommen hetzelfde over de verschillende tabellen
gapminderDf$country <- as.character(gapminderDf$country)
tidyFlu$Date <- as.numeric(substr(tidyFlu$Date,1,4))
tidyDengue$Date <- as.numeric(substr(tidyDengue$Date,1,4))

# kijk of de datatypes nu overeenkomen en verken verder de data
summary(tidyDengue)
summary(tidyFlu)
summary(gapminderDf)
```

```{r, eval=FALSE}
# sla de gecleande data op
write_csv(tidyFlu, here("assignment7", "tidyFlu.csv"), row.names = FALSE)
write_csv(tidyDengue, path= here("assignment7", "tidyDengue.csv"), append=FALSE)
write_csv(gapminderDf, path= here("assignment7", "gapminderDf.csv"), append=FALSE)
write_rds(tidyFlu, path= here("assignment7", "tidyFlu.rds"), append=FALSE)
write_rds(tidyDengue, path= here("assignment7", "tidyDengue.rds"), append=FALSE)
write_rds(gapminderDf, path= here("assignment7", "gapminderDf.rds"), append=FALSE)
```

```{r, eval=FALSE}
# maak een con object als connectie maar dan met het eigen wachtwoord
con <- dbConnect(RPostgres::Postgres(),
                 dbname = "workflowsdb",
                 host="localhost",
                 port="5432",
                 user="postgres",
                 password="password")

# laad de tabellen in de database in
dbWriteTable(con, "tidyFlu", read_csv(here("assignment_7", "tidyFlu.csv")))
dbWriteTable(con, "tidyDengue", read_csv(here("assignment_7", "tidyDengue.csv")))
dbWriteTable(con, "gapminderDf", read_csv(here("assignment_7", "gapminderDf.csv")))
```

5. In Dbeaver create a new PostgreSQL database “workflowsdb”

6. Using RPostgreSQL, insert the tables into the database.

7. Inspect the contents of the tables with SQL (in DBeaver) and save the SQL script.

8. Inspect the contents of the tables with dplyr (in R) and save a RMarkdown showing what you are doing.

9. Load the gapminder data in R and change the dataframe in such as way that you could join it to dengue and flu.

10. Save this clean gapminder data in the “workflowsdb” database

11. Perform some joins (your choice) with SQL (can be done in DBeaver or with dplyr.

12. Generate a joined table, and export this from the database to R.

13. Show some descriptive statistics with this table, and at least 3 visualisations using ggplot2.

14. Write a short report to show at least the actions listed in this assignment in a Rmd file for your portfolio. Include pictures and provide text explaining and showcasing your skills.
