---
title: "assignment_3"
author: "Wouter"
date: '2022-05-09'
output: html_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Assignment 8
In deze opdracht moet een r package gemaakt worden. 

### de opdracht:
your new package should at least include:

1) A properly formatted DESCRIPTION file with all the fields including relevant information (so change the default values), 

2) 4 different functions that you wrote and with proper documentation, using roxygen2 comments, 

3) A NAMESPACE file, generated with the command devtools::document(), 

4) 1 Raw dataset that is documented and cleaned into a clean dataset. This clean dataset should be accessible inside your package. This means that if I install your package from Github, I would be able to call data(<dataset_name>, <package_name>) to load the cleaned dataset of interest in the Global Environment, 

5) One vignette that is accessible via the command browseVignettes(<package_name>) or vignette(<package_name>), 

6) The package installs from Github without errors when I run: devtools::install_github("account_name/package_name")

### resultaat:
Voor het package zie repository: explorers op profile: WouterVerra
zie ook de soccer dataset die bijgevoegd is aan de package.

```{r eval=FALSE}
devtools::install_github("WouterVerra/explorers", build_vignettes = TRUE)
```

