---
title: "assignment_9"
author: "WouterVerra"
date: "`r Sys.Date()`"
output: html_document
params:
  country: "Austria"
  year: 2022
  month: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
```

# parameterization of Rmarkdown documents

```{r, eval=FALSE}
# onuitgevoerd blok om makkelijk zelf de parameters van dit bestand aan te passen
rmarkdown::render(here("assignment_9", "assignment_9.Rmd"), params = list(country = "Greece", year = 2021, month = 6))
```

# Assignment 9
In deze opdracht moet een rmarkdown gemaakt worden met parameters die je kunt aanpassen waardoor de output van de rmarkdown veranderd. 

### de opdracht:
The aim of this assignment is to create an RMardown file containing a parameterized report for the COVID-19 cases as can be downloaded from the ECDC. The Rmd should include at least three parameters:

The country to which the report applies to, The year that the reported data applies to, The period in months that the report applies to.

Here is where you can find the ECDC data: [here](https://www.ecdc.europa.eu/en/covid-19/data)

The minimum requirements for the report is that next to the three parameters mentioned above, it should include at least one graph for the COVID-19 cases and one graph for the COVID-19 related deaths. After writing the Rmd, you should be able to render it with parameters set to any value you like.

```{r}
# read  in csv with covid data
covid_data <- read.csv(here("assignment_9", "data.csv"))

# filter op land
covid_data <- covid_data %>% filter(countriesAndTerritories == params$country)

# filter op jaar
covid_data <- covid_data %>% filter(year == params$year)

# filter op maand
covid_data <- covid_data %>% filter(month == params$month)

# plot the cases
covid_data %>% 
  ggplot(aes(x= day, y= cases)) +
  geom_line() +
  geom_point() +
  labs(title= paste0("Covid 19 cases in: ", params$country, " in: ", params$month, "/", params$year), y= "Covid cases")

# plot the deaths
covid_data %>% 
  ggplot(aes(x= day, y= deaths)) +
  geom_line() +
  geom_point() +
  labs(title= paste0("Covid 19 deaths in: ", params$country, " in: ", params$month, "/", params$year), y= "Covid deaths")
```

